% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Milan Gvero}
\address{Vojvodjanska 2b\linebreak 21000 Novi Sad, Serbia}
\contacts{(+381)60 414 85-85\linebreak mgstivig585@gmail.com}

\begin{document}

	% Print the header
	\makeheader

	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Scholarship - BSc}{iWedia S.A}{August 2018 - October 2018}
			Beeline - TV Everywhere:
			\begin{itemize}
				\item Worked on creating offline demo mode for Beeline STB app, with same featrue set as base online app.
				\item Fully responisble for creating and delivering new releases and instructions to client.
				\item Responsible for preparing stb for various conferences (Las Vegas, Amsterdam, etc..)
				\item Published and presented papar on this topic at Telfor conference in Belgrade.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Scholarship - MCs}{iWedia S.A}{May 2019 - July 2019}
			Beeline - TV Everywhere:
			\begin{itemize}
				\item Implemented web server on STB needed for google cast like feature (casting media from phone to STB) using Restlet framework.
				\item Worked on discovery and pairing for STB and mobile by follwing UPnP and SSDP protocols.
				\item Added usefull debug and test endpoints for testing casting and displaying useful debug data from stb.
				\item Published and presented papar on this topic at Etran conference in Silver Lake Resort.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Junior Java Software Engineer}{iWedia S.A}{July 2019 - December 2019}
			Beeline - TV Everywhere:
			\begin{itemize}
				\item Mostly worked on features for application level side in stb aosp app.
				\item Worked as support for features and fixes for android tv app.
				\item Created releases and ota images for client using Jenkins.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Junior/Medior Java/C++ Software Engineer}{iWedia S.A}{December 2019 - Today}\vspace{\baselineskip}
			Beeline - TV Everywhere:
			\begin{itemize}
				\item Started to work on Iwedia's middleware stack and OTT player which is used in Beeline app for 1+ million customers.
				\item Worked on adding multi-period feature for dash streaming protocol.
				\item Added support for subtitles (webvtt, ttml), and multi-audio support (changing tracks, support for dolby), both on player and application side.
				\item Supported various aosp patches from 3 different vendors, using custom toolchains, and building android from scrach.
				\item Creating and maintaining various Jenkins jobs (release pipelins, nightly jobs, etc).
				\item Worked in parallel for same operator but in Kazakhstan.
				\item Partially ported Iwedia's new R\&D baked C++14 OTT player to Beeline app. 
				\item Worked in multinational team (4 countries).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Serbia, Novi Sad}{Faculty of Technical Sciences}{2014 -- 2019}
			\begin{itemize}
				\item B.S.E. in Electrical and Computer Engineering, May 2018. GPA: 8.54/10
				\item M.S.E. in Electrical and Computer Engineering, May 2019. GPA: 9.75/10
				\item Graduate \& Undergraduate Coursework: Mathematical Analysis I \& II, Algebra, Programming Languages and Data Structures,
				Fundamentals of Electrical Engineering, Computer Architecture, System Modeling and Simulation, Logic Design of Computer Systems,
				Object Oriented Programming, Operating Systems, Automatic Control Systems, Real Time System Programming, Probability and Stochastic Processes,
				Optimization Method, Databases, Fundamentals of Computer Networks, Fundamentals of DSP Architecture and Algorithms,
				Web Programming, Dedicated Computer Structure Design, Digital Televison I \& II.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			Some projects that were made at college/free time  - https://github.com/Gvex95
			\begin{itemize}
				\item \textbf{Android\_TaskManager\_College} - Android task manager app made for college project.
				\item \textbf{bubble-bobble} - Python implementation of bubble-bobble game, made with qt (non-finished).
				\item \textbf{YARA} - Reminder App (Not started, but idea is to create this simple app in order to learn android jetpack framework).
				\item \textbf{grow-grow-piggies} - Simple android app used to help people on countryside when feeding cattle.
				\item \textbf{RealDebridPlayer} - Android TV app which should display various trending movies/tv shows from trakt,
	and allow user to play it from real-debrid servers using exo player. Intended as project for learning newest android tools and design patterns. (Due to lack of time, not yet started).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item C++; C; Java; Python;
				\item Gradle; GCC; Adb; Aosp;
				\item Git/Gerrit; Jenkins; Docker;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
